Stack Safety is a Security Property

### 2021-04-14 tex/main.tex
Simple properties stated

Next we consider {\em lockstep stack confidentiality}. Here it behooves us to factor out
the general notion of lockstep confidentiality independent of a particular context model.

\subsection{Eager Confidentiality}

@@

\definition Machine state pairs \(\mach,\mach'\) and \(\nach,\nach'\) have the {\em same differences}
if for all components \(\component\) such that \(\mach ~ \component \not = \mach' ~ \component\) or
\(\nach ~ \component \not = \nach' ~ \component\), \(\mach' ~ \component = \nach' ~ \component\).
This is written \(\mach,\mach' \diamond \nach,\nach'\).

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \depth')\) hold for
\(\depth' \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\depth)\) and
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component \not = \outside\).
Then take any \(\nach\) such that \(\mach \approx_\components \nach\). \(\MPCT\) corresponds to the
trace of a subroutine from its call to its return.

If we take the induced trace from this variant until a return,
\(\nach,\pol,\context \hookrightarrow \NPCT | \neg f_\depth\), we get a subtrace corresponding
to the same subrouting called with the same (register) arguments but with a potentially different
state at the call-site. A system enjoys {\em eager confidentiality} if for all such pairs of traces,
they correspond according to one of four cases:

\begin{enumerate}
\item \(\MPCT\) may be finite and \(\pi_\context(\last(\MPCT)) = (\_,\depth')\) with \(\depth' < \depth\),
  and \(\pi_\context(\last(\NPCT)) = (\_,\depth')\) with \(\depth' < \depth\). That is, both traces end
  having left the call of depth \(\depth\). Further:
  \begin{itemize}
  \item They have the same observable behavior, \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
  \item Their final states have the same differences:
    \[\pi_\mach(\head(\MPCT)), \pi_\mach(\last(\MPCT)) \diamond
    \pi_\mach(\head(\MPCT)), \pi_\mach(\last(\NPCT))\]
  \end{itemize}
\item \(\MPCT\) and \(\NPCT\) may both be infinite, with \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
\item \(\MPCT\) may be finite but end without returning -- which can only have happened if it fail-stopped --
  and its observable behavior prefixes that of \(\NPCT\), \(\pi_\obs(\MPCT) \lesssim \pi_\obs(\NPCT)\)
\item \(\NPCT\) may end with a fail-stop as in case 3, with \(\pi_\obs(\NPCT) \lesssim \pi_\obs(\MPCT)\)
\end{enumerate}

\subsection{Trace Properties}

Having seen instances of eager confidentiality and integrity, defined in terms of reachable trace
segments, we can generalize them to properties of the trace segments themselves. Then as we expand
our model, our further properties will be defined in terms of the trace properties.

\definition Let \(\MPCT\) be a reachable segment and \(\components\) be any set of components.
\(\MPCT\) enjoys {\em trace integrity} when \(\last(\MPCT) ~ \component = \head(\MPCT) ~ \component\)
for all \(\component \in \components\), and when \(\last(\MPCT)\) is undefined.

\definition Let \(\MPCT \langle f \rangle\) be a reachable segment delimited by the predicate \(f\)
and the \(\components\) be any set of components. Let \(\head(\MPCT) = \mpcstate{\mach}{\pol}{\context}\)
and \(\nach\) be a machine state such that \(\mach \approx_\components \nach\). Suppose we take the
induced trace from \(\npcstatename = \mpcstate{\nach}{\pol}{\context}\) that corresponds to \(\MPCT\),
\(\npcstatename \hookrightarrow \NPCT | \neg f\). The trace \(\MPCT\) enjoys {\em trace confidentiality}
with respect to \(f\) and \(P\) if, for all such \(\NPCT\), they correspond according to the four cases
above:

\begin{enumerate}
\item \(\MPCT\) may be finite and \(\pi_\context(\last(\MPCT)) = (\_,\depth')\) with \(\depth' < \depth\),
  and \(\pi_\context(\last(\NPCT)) = (\_,\depth')\) with \(\depth' < \depth\). That is, both traces end
  having left the call of depth \(\depth\). Further:
  \begin{itemize}
  \item They have the same observable behavior, \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
  \item Their final states have the same differences:
    \[\pi_\mach(\head(\MPCT)), \pi_\mach(\last(\MPCT)) \diamond
    \pi_\mach(\head(\MPCT)), \pi_\mach(\last(\NPCT))\]
  \end{itemize}
\item \(\MPCT\) and \(\NPCT\) may both be infinite, with \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
\item \(\MPCT\) may be finite but end without returning -- which can only have happened if it fail-stopped --
  and its observable behavior prefixes that of \(\NPCT\), \(\pi_\obs(\MPCT) \lesssim \pi_\obs(\NPCT)\)
\item \(\NPCT\) may end with a fail-stop as in case 3, with \(\pi_\obs(\NPCT) \lesssim \pi_\obs(\MPCT)\)
\end{enumerate}

>>>>

Next we consider {\em stepwise stack confidentiality}. There are a number of preliminary
concepts we must discuss here -- confidentiality quantifies over {\em variants} of the
initial state of a call, and requires that the traces from them move in {\em lockstep}.

@@

\definition Machine state pairs \(\mach,\mach'\) and \(\nach,\nach'\) are {\em synched}
if for all components \(\component\) such that \(\mach ~ \component \not = \mach' ~ \component\) or
\(\nach ~ \component \not = \nach' ~ \component\), \(\mach' ~ \component = \nach' ~ \component\).
This is written \(\mach,\mach' \diamond \nach,\nach'\).

\definition A pair of traces \(\machT\) and \(\nachT\) are {\em in lockstep} if their adjacent pairs
are synched, written as a coinductive relation \(\machT \doteq \nachT\):

\begin{minipage}{.3\textwidth}
\judgment{}
         {\(\mach \doteq \nach\)}
\end{minipage}
\begin{minipage}{.6\textwidth}
\judgmenttwo{\(\mach, \head(\machT) \diamond \nach, \head(\nachT)\)}
            {\(\machT \doteq \nachT\)}         
            {\(\mach \machT \doteq \nach \nachT\)}
\end{minipage}

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \depth')\) hold for
\(\depth' \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\depth)\) and
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component \not = \outside\).
\(\MPCT\) corresponds to the trace of a subroutine from its call to its return.
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).
